\documentclass{article}
\usepackage[utf8]{inputenc}

\title{ada-seregin conception}
\author{Alex Seregin}
\date{April 2022}

\begin{document}

\maketitle
\section{Abstract}
Formulating a novel description of the evolutionary process in a well-defined environment will allow detailed exploration how value is created and has implications in [economics, business, social sciences]
\section{Introduction}
I know not you and you know not me, and no one knows one self.
In essence, my work is Strong Story Hypothesis expressed in terms of Origins of Wealth theory using Barbasi-Albert model.

\section{Definitions}
\subsection{Environment}
A multidimensional bipartite scale-free multigraph $\Re$ (Cardano)

$\Theta$: set of minds, in which a node $\epsilon$ is described by the set of parameters $\xi$ (KSA) and personal capital $\rho$ and age A.

$\Gamma$: set of ideas, or memes. Ideas $\iota$ relate to each other by distance $\omega$ and are combined loosely into sciences, areas, domains, subdomains, topics, concepts, definitions, etc.

DAO: a cluster of $\epsilon$ characterised by relations such as ([word], how easy or hard the information flow is) is below a certain threshold (simplified, to define, see networks-book.pdf); and shared capital $\tau$ = f($\rho$) of the nodes in the cluster.

Personal idea space $\gamma$ is defined for each node as a parameter in $\xi$ as a person's access to domains of knowledge and the quality of links to it. 
Shared idea space is defined for a DAO and is a function of access to the shared idea space by each of the nodes

\subsection{The process}
At each step several things happen:
1. Personal capital is consumed by each node. 
2. $\xi$ for each $\epsilon$ has a chance to change.
3. A business plan $\kappa$ has a chance of being created. The chance is determined by a set of characteristics of the DAO: quality of share idea space and characteristics of the cluster (information flow, efficiency, quality of community, mission, values, how networked the cluster is, etc.)
4. If $\tau$ is below a certain threshold, the cluster has a chance to dissolve.
5. Each node has a chance to expire as a function of A

\subsection{A business plan}
$\kappa$ is characterised by a fitness function $\lambda$ that is stochastic, and depends on the characteristics of the parent cluster, and a lifetime L.

At each step each idea has a chance to \textbf{\textit{flower}} or will expire upon reaching its limits.
A flowered idea will create some capital that gets distributed between nodes according to some rules (like how old they are, what is their weight and centrality, or other importance measures) and such promotes operation of a DAO

\section{Questions}
It would be nice to know how Bayes theorem can be implemented in description of the personal and share idea space.

\section{Consequences and expected behavior}
A dissolved cluster is a source of powerful nodes that seed new clusters as a function of their parameters.

\section{Sources}
1. Albert-Barabasi model, 
2. Origins of Wealth
3. Strong Story Hypothesis
4. Society of Mind
5. How to grow a mind?
6. Steven Strogatz, Dynamical Systems and Chaos
7. Feldman, Santa Fe
8. Networks, Crowds and Markets
9. Games and Information
10. The Resilient Society
11. maybe more, I am not sure I can find exact quotes in all these. 
\section{Authors}
[alexeusgr, $[50^2]$ and BJ] in Alex Seregin, ADAO Community, Cardano Blockchain. 
\section{Mentors and Reviewers}
Alussian, Quasar, Benjamin Hackl, Ninh Tran, Kevin M., Michael C., Randall, James Duneith, Staske 

\end{document}
